What is more important than the earth itself?

One's mother.\medskip

What is higher than heaven?

One's father.\medskip

What is swifter than wind?

The mind.\medskip

More numerous than the blades of grass?

The thoughts in the mind.\medskip

What is the highest sanctuary of Dharma?

Liberality.\medskip

What is the highest sanctuary of fame?

A gift.\medskip

Of heaven?

The truth.\medskip

What is the most praiseworthy thing of all?

Skill.\medskip

The most valuable possession?

Knowledge.\medskip

The greatest treasure?

Health.\medskip

The greatest happiness?

Contentment.\medskip

What is the highest Dharma?

To injure none of the living.\medskip

What must be controlled?

The mind.\medskip

What renounce to make a man agreeable?

Pride.\medskip

What renounce to make a man wealthy?

Desire.\medskip

And what can be renounced without regret?

Anger.\medskip

And what will be relinquished to gain happiness?

Greed.\medskip

What makes the way?

The good make the way, indeed they are the way.\medskip

Who is the ascetic?

He who remains faithful.\medskip

What is true restraint?

That of the mind.\medskip

And what is true forgiveness?

He who endures enmity truly forgives.\medskip

What is real knowledge?

The knowledge of god.\medskip

What is tranquility?

When the heart is still.\medskip

What is mercy?

When one desires the happiness of all creatures.\medskip

What is simplicity?

When the heart is tranquil.\medskip

What is the invincible enemy?

Anger.\medskip

What disease has no cure?

Covetousness.\medskip

What is the honest man?

He who desires the happiness of all the living.\medskip

And the dishonest one?

The one who has no mercy.\medskip

What is ignorance?

Not knowing one's Dharma.\medskip

What is pride?

When a man thinks that he's the one who is the doer of life.\medskip

What is grief?

Only ignorance.\medskip

How does a man become patient?

By subduing his senses.\medskip

Which is the true ablution?

When the heart is washed clean.\medskip

What is charity?

Protecting all creatures.\medskip

What is wickedness?

Speaking ill of others.\medskip

How is a man agreeable?

When he speaks agreeably.\medskip

How does he get what he wants?

When he acts with discernment.\medskip

And how does he find bliss in the next world?

By being virtous in this one.\medskip

Who is the real man?

Word of one's good deeds reach heaven and are spread from there across the earth. As long as that word lasts, one is called a man.\medskip

Who is he Yudhishthira, who has every kind of walth?

Only he to whom joy and sorrow, fortune and misfortune, past and future are all the same.\medskip
