\vspace*{1.2cm}
\textbf{What is more important than the earth itself?}

\textit{One's mother.}\medskip

\textbf{What is higher than heaven?}

\textit{One's father.}\medskip

\textbf{What is swifter than wind?}

\textit{The mind.}\medskip

\textbf{More numerous than the blades of grass?}

\textit{The thoughts in the mind.}\medskip

\textbf{What is the highest sanctuary of Dharma?}

\textit{Liberality.}\medskip

\textbf{What is the highest sanctuary of fame?}

\textit{A gift.}\medskip

\textbf{Of heaven?}

\textit{The truth.}\medskip

\textbf{What is the most praiseworthy thing of all?}

\textit{Skill.}\medskip

\textbf{The most valuable possession?}

\textit{Knowledge.}\medskip

\textbf{The greatest treasure?}

\textit{Health.}\medskip

\textbf{The greatest happiness?}

\textit{Contentment.}\medskip

\textbf{What is the highest Dharma?}

\textit{To injure none of the living.}\medskip

\textbf{What must be controlled?}

\textit{The mind.}\medskip

\textbf{What renounce to make a man agreeable?}

\textit{Pride.}\medskip\vfill\pagebreak\vspace*{1.2cm}

\textbf{What renounce to make a man wealthy?}

\textit{Desire.}\medskip

\textbf{And what can be renounced without regret?}

\textit{Anger.}\medskip

\textbf{And what will be relinquished to gain happiness?}

\textit{Greed.}\medskip

\textbf{What makes the way?}

\textit{The good make the way, indeed they are the way.}\medskip

\textbf{Who is the ascetic?}

\textit{He who remains faithful.}\medskip

\textbf{What is true restraint?}

\textit{That of the mind.}\medskip

\textbf{And what is true forgiveness?}

\textit{He who endures enmity truly forgives.}\medskip

\textbf{What is real knowledge?}

\textit{The knowledge of god.}\medskip

\textbf{What is tranquility?}

\textit{When the heart is still.}\medskip

\textbf{What is mercy?}

\textit{When one desires the happiness of all creatures.}\medskip

\textbf{What is simplicity?}

\textit{When the heart is tranquil.}\medskip

\textbf{What is the invincible enemy?}

\textit{Anger.}\medskip

\textbf{What disease has no cure?}

\textit{Covetousness.}\medskip

\textbf{What is the honest man?}

\textit{He who desires the happiness of all the living.}\medskip\vfill\pagebreak\vspace*{1.2cm}

\textbf{And the dishonest one?}

\textit{The one who has no mercy.}\medskip

\textbf{What is ignorance?}

\textit{Not knowing one's Dharma.}\medskip

\textbf{What is pride?}

\textit{When a man thinks that he's the one who is the doer of life.}\medskip

\textbf{What is grief?}

\textit{Only ignorance.}\medskip

\textbf{How does a man become patient?}

\textit{By subduing his senses.}\medskip

\textbf{Which is the true ablution?}

\textit{When the heart is washed clean.}\medskip

\textbf{What is charity?}

\textit{Protecting all creatures.}\medskip

\textbf{What is wickedness?}

\textit{Speaking ill of others.}\medskip

\textbf{How is a man agreeable?}

\textit{When he speaks agreeably.}\medskip

\textbf{How does he get what he wants?}

\textit{When he acts with discernment.}\medskip

\textbf{And how does he find bliss in the next world?}

\textit{By being virtous in this one.}\medskip

\textbf{Who is the real man?}

\textit{Word of one's good deeds reach heaven and are spread from there across the earth. As long as that word lasts, one is called a man.}\medskip

\textbf{Who is he Yudhishthira, who has every kind of walth?}

\textit{Only he to whom joy and sorrow, fortune and misfortune, past and future are all the same.}\medskip
